Galaxy Zoo: Classifications for Galaxies in HST Legacy Imaging

### 2014-03-04 writeup/gz_hubble_data.tex
Put fake results in as .ps

\subsection{Selection of Input Galaxies}

\includegraphics[width=0.49\textwidth]{fake_results.pdf}

\caption{Fake results of the FERENGI redshifting exercise. For three vote fraction levels and thee surface-brightness levels each, we show the evolution of the 7 evolutionary corrections used with redshift.}

@@

>>>>

\subsection{Selection of FERENGI Input Galaxies}

@@

\subsection{Results of FERENGI Analysis}

We show here the {\bf currently fake} results of citizen scientist classifications of images of galaxies placed at artificial redshifts. Figure \ref{results1} shows the {\bf currently fake} change of vote fractions for feature X with redshift, for three vote fraction levels with three surface-brightness levels and 7 evolutionary corrections.

\includegraphics[width=0.35\textwidth,angle=90]{fake_results.ps}

\caption{Fake results of the FERENGI redshifting exercise. For three vote fraction levels with three surface-brightness levels and 7 evolutionary corrections each, we show the evolution of the vote fractions for feature X with redshift.}
